\sysfull

### 2018-08-07 paper/asplos19/background.tex
revisions of background

\begin{table}
    \centering
    \footnotesize
    \begin{tabular}{|c|c|}
        \hline
        Model & Data Copied to/from NVRAM \\
        \hline\hline
        Mementos~\cite{mementos}    & Registers + Stack     \\
        DINO~\cite{dino}    & Registers + Stack + WAR NV variables \\%used in task\\
        Chain~\cite{chain}  & PC + NV variables used in task\\
        Alpaca~\cite{alpaca}    & PC + WAR NV variables used in task\\
        Ratchet~\cite{ratchet}, Clank~\cite{hicks_isca_2017} & Registers (requires NV main memory) \\
        Region Formation~\cite{baghsorkhi_cgo_2018} & Registers + Updated variables in task \\
        \hline
    \end{tabular}
    \caption{Non-volatile memory access for data consistency; \emph{PC}: program counter, \emph{WAR variables}: variables involved in Write after Read (WAR) dependences, \emph{NV}: non-volatile.}
    \label{table:chechpoint_comparison}
\end{table}

@@

\paragraph{Incorrectly Sized Tasks.}
Compiler-inserted checkpoints or programmer-defined tasks can be both non-terminating and/or inefficient.  If a task (or code between two checkpoints) consumes more than the fixed, maximum energy that the device can buffer, then the task will never be able to complete using buffered energy only.  Such a task is non-terminating, {\em prevents forward progress}, and makes the program deadlock. If the task consumes far less energy than a device can buffer, the system may operate {\em inefficiently}, saving the program state more often than needed. Avoiding excessively costly, non-terminating tasks and short, high-overhead tasks is challenging, because estimating the exact energy use of an arbitrary code is complicated. Moreover, when \emph{heterogeneous devices} with different energy buffers (e.g., 20 \si{\micro\farad}~\cite{rodriguez_tbcs_2015} to 0.1 \si{\farad}~\cite{moo}) are considered, the problem of porting a program becomes much worse because a large task on one device may be a relatively short task on a device with a larger buffer. \textbf{\sys's execution model} solves this dilemma by introducing {\em task coalescing}, which merges multiple tasks to amortize the overhead when tasks are too small, and {\em task downscaling}, which breaks up a task when it is too large to complete.

>>>>

\begin{table}
    \centering
    \footnotesize
    \begin{tabular}{|c|c|}
        \hline
        Model & Data Copied to/from NVRAM \\
        \hline\hline
        Mementos~\cite{mementos}    & Registers + Stack     \\
        DINO~\cite{dino}    & Registers + Stack + WAR NV variables \\%used in task\\
        Chain~\cite{chain}  & PC + NV variables used in task\\
        Alpaca~\cite{alpaca}    & PC + WAR NV variables used in task\\
        Ratchet~\cite{ratchet}, Clank~\cite{hicks_isca_2017} & Registers (requires NV main memory) \\
        Region Formation~\cite{baghsorkhi_cgo_2018} & Registers + Updated variables in task \\
        \hline
    \end{tabular}
    \caption{Non-volatile memory access for data consistency; {PC}: program counter, {WAR variables}: variables involved in Write-after-Read (WAR) dependencies, {NV}: non-volatile.}
    \label{table:chechpoint_comparison}
\end{table}

@@

\paragraph{Incorrectly Sized Tasks.}
Compiler-inserted checkpoints or programmer-defined tasks can be both non-terminating and/or inefficient.  If a task (or code between two checkpoints) consumes more than the fixed, maximum energy that the device can buffer, then the task will never be able to complete using buffered energy only.  Such a task is non-terminating, {\em prevents forward progress}, and makes the program deadlock. If the task consumes far less energy than a device can buffer, the system may operate {\em inefficiently}, saving the program state more often than needed. Avoiding excessively costly, non-terminating tasks and short, high-overhead tasks is challenging, because estimating the exact energy use of an arbitrary code is complicated. Moreover, when \emph{heterogeneous devices} with different energy buffers (e.g., 20 \si{\micro\farad}~\cite{rodriguez_tbcs_2015} to 0.1 \si{\farad}~\cite{moo}) are considered, the problem of porting a program becomes much worse because a large task on one device may be a relatively short task on a device with a larger buffer. \sys's \emph{execution model} solves this dilemma by introducing {\em task coalescing}, which merges multiple tasks to amortize the overhead when tasks are too small, and {\em task downscaling}, which breaks up a task when it is too large to complete.
